\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-10-03 paper.tex
wrote the abstract

\begin{abstract}
	% abstract goes here
	% TODO write abstract
\end{abstract}

@@

Our team consists of three Senior Worcester Polytechnic Institute (WPI)
students: William Campbell, computer science and interactive media and game
development double major; Cole Granof, computer science major; and Joseph
Petitti, computer science major. We spent twelve weeks in Shiga, Japan
completing the requirements for our Major Qualifying Project, a WPI graduation
requirement in which students solve a real-world problem through practical
project-based work. Our project was sponsored by Kyoto~VR, a startup founded in
2016 to ``document and preserve the culture and heritage of the city and
communicate the richness of Japan’s Old Capital to the
world''~\autocite{kyotovr2018}.

Our team worked directly under Kyoto VR founder and CEO Atticus Sims to develop
and tested a mobile app to deliver an audio tour, incorporating various
augmented reality (AR) features to enhance the experience. Our app delivers a
tour of Kinkaku-ji, or The Temple of the Golden Pavilion, a popular tourist
destination in Kyoto. In this app, which we call ARuko, many of the AR features
were aimed at improving accessibility. These features include translating signs
and providing additional info on the physical map located at the site. Other
features were purely for spectacle, such as the ability to take an AR
``souvenir'' home by scanning the ticket to enter Kinkaku-ji.

@@

Since our app had to deliver an audio tour supplemented by images based on your
latitude and longitude, we developed an internal tool to design physical
regions for each step of the tour. This tool, called Editour provides a rich
editing suite through a simple web interface. Section~\ref{sec:editingATour}
goes into detail about the features of this web app. We also wrote a backend to
manage the tour files, allowing one of us (or our sponsor, Atticus Sims) to
download a zip file containing all of the media and info to reconstruct the
tour. This zip can be extracted into the source files for ARuko, which rebuilds
the tour from the downloaded contents. We were able to host the backend on the
server provided by Kyoto~VR's hosting plan; we discuss the hurdles that we
overcame to deploy the Editour backend with Kyoto~VR's current setup in
Section~\ref{sec:deployingTheEditourBackend}.

>>>>

\begin{abstract}
Kinkaku-ji, the Temple of the Golden Pavilion, is one of Kyoto's most visited
tourist attractions. Most people who visit the site do not have the opportunity
to experience the rich art and culture that are part of its history. We worked
with our sponsor, Kyoto VR, to create an app that would allow visitors of 
Kinkaku-ji to better experience these aspects of the site. We used Unity to
create an audio tour app that provides historical insight on the location, 
displays galleries of art throughout the visit, and offers accessibility 
features through AR. We hope our app will enhance the experience of visiting
Kinkaku-ji.  
\end{abstract}

@@

Our team consists of three Senior Worcester Polytechnic Institute (WPI)
students: William Campbell, computer science and interactive media and game
development double major; Cole Granof, computer science major; and Joseph
Petitti, computer science major. We spent twelve weeks in Shiga prefecture, Japan,
completing the requirements for our Major Qualifying Project, a WPI graduation
requirement in which students solve a real-world problem through practical
project-based work. Our project was sponsored by Kyoto~VR, a startup founded in
2016 to ``document and preserve the culture and heritage of the city and
communicate the richness of Japan’s Old Capital to the
world''~\autocite{kyotovr2018}.

Our team worked directly under Kyoto VR founder and CEO Atticus Sims to develop
and test a mobile app to deliver an audio tour, incorporating various
augmented reality (AR) features to enhance the experience. Our app delivers a
tour of Kinkaku-ji, or The Temple of the Golden Pavilion, a popular tourist
destination in Kyoto. In this app, which we call ARuko, many of the AR features
were aimed at improving accessibility. These features include translating signs
and providing additional info on the physical map located at the site. Other
features were purely for spectacle, such as the ability to take an AR
``souvenir'' home by scanning the ticket to enter Kinkaku-ji.

@@

Since our app had to deliver an audio tour supplemented by images based on your
latitude and longitude, we developed an internal tool to design physical
regions for each step of the tour. This tool, called Editour, provides a rich
editing suite through a simple web interface. Section~\ref{sec:editingATour}
goes into detail about the features of this web app. We also wrote a backend to
manage the tour files, allowing one of us (or our sponsor, Atticus Sims) to
download a zip file containing all of the media and info to reconstruct the
tour. This zip can be extracted into the source files for ARuko, which rebuilds
the tour from the downloaded contents. We were able to host the backend on the
server provided by Kyoto~VR's hosting plan; we discuss the hurdles that we
overcame to deploy the Editour backend with Kyoto~VR's current setup in
Section~\ref{sec:deployingTheEditourBackend}.
